NFC and burnout in teachers - A replication and extension study

### 2021-09-10 Manuscript/Manuscript.Rmd
changed some details

```{r import, echo=FALSE, message=FALSE, warning=FALSE}
  # Define the top level as the one where this file lies
  # If the rest of the files follow the structure of the Github project, everything will work

@@

## Material
All questionnaires were used in their German form. Burnout was assessed using the 21-item Maslach Burnout Inventory (MBI) [@Buessing1992], NFC was assessed using the 16-item Need for Cognition Scale (NCS) [@Bless1994], self-control was assessed using the 13-item Self-Control Scale (SCS) [@Bertrams2009a], reappraisal and suppression were assessed using the 10-item Emotion Regulation Questionnaire (ERQ) [@Abler2009], work satisfaction was assessed using the Allgemeine Arbeitszufriedenheit questionnaire (AAZ) [@Fischer2014].
Eleven items were created to assess each participant's current burden by the Covid-19 pandemic, such as whether they belong to a risk group or whether they currently have a higher workload.
The Covid-19 items can be found in the **Supplementary Material**.
The survey also included the Subjective Wellbeing Index of the World Health Organization [@Braehler2007], which we will not analyze.
Due to a technical error during survey setup, the coping style data of the Erfurter Belastungsinventar [@BoehmKasper2001] cannot be used, so we cannot replicate the mediation of NFC and burnout by active and passive coping.

@@

### *Structural equation model*
Items were reverse coded according to the scale manuals.
The latent factor NFC was computed by subjecting the NCS items to a parcelling procedure following Grass et al. [-@Grass2019], a method that is used in SEM when only relations between but not within constructs are of interest.
Principal component analysis was used to determine the factor loadings of each NCS item onto the first component.
Then, the items were randomly divided into four parcels and the average item loading per parcel was computed.
This was repeated 10,000 times to find the parcelling choice with the smallest difference in average item loadings between parcels.
The latent factor MBI was computed using the three subscales as indicators.
For the demand-resource-ratios, we used three items from the work satisfaction scale each, without reverse coding them.
The latent factor DTH was indicated by items 4, 8, and 9, DTL by items 12, 26, and 27, and DRF by items 17, 22, and 24.

@@

  mbi[,keylist$mbi_rpe] <- 7 - mbi[,keylist$mbi_rpe]  # Recode from 1-6 to 6-1
  scs[,keylist$scs] <- 6 - scs[,keylist$scs]          # Recode from 1-5 to 5-1
  scs <- scs - 3                                      # Recode all from 1-5 to -2-+2
  ncs[,keylist$ncs] <- 8 - ncs[,keylist$ncs]          # Recode from 1-7 to 7-1
  ncs <- ncs - 4                                      # Recode all from 1-7 to -3-+3
  ws[,keylist$ws] <- 6 - ws[,keylist$ws]              # Recode from 1-5 to 5-1
  ws <- ws - 3                                        # Recode all from 1-5 to -2-+2
  covb[,c(2,3,4,9)] <- 4 - covb[,c(2,3,4,9)]          # Recode from 1-3 to 3-1
  covb[,8] <- 3 - covb[,8]                            # Recode from 1-2 to 2-1
  dth <- 6 - dth
  dth <- dth - 3                                      # Recode all from 1-5 to to -2-+2
  dtl <- dtl - 3                                      # Recode all from 1-5 to to -2-+2
  drf <- 6 - drf
  drf <- drf -3                                       # Recode all from 1-5 to to -2-+2

@@

  # Remove participant 161
  score_data <- score_data[score_data$mbi < 100, ]

@@

  # structural model
    DTH ~ NFC
    DTL ~ NFC
    DRF ~ NFC
    RPE ~ NFC + DTH + DTL + DRF'

>>>>

```{r import, echo=FALSE, message=FALSE, warning=FALSE}
  # Define the top level as the one where this file lies
  # If the rest of the files follow the structure of the Github repository, everything will work
  # (Simply download the entire repository to any location on your computer)

@@

## Material
All questionnaires were used in their German form.
Burnout was assessed using the 21-item Maslach Burnout Inventory (MBI) [@Buessing1992], NFC using the 16-item Need for Cognition Scale (NCS) [@Bless1994], self-control using the 13-item Self-Control Scale (SCS) [@Bertrams2009a], reappraisal and suppression using the 10-item Emotion Regulation Questionnaire (ERQ) [@Abler2009], and work satisfaction using the Allgemeine Arbeitszufriedenheit questionnaire (AAZ) [@Fischer2014].
Eleven items were created to assess each participant's current burden by the Covid-19 pandemic, such as whether they belong to a risk group or whether they currently had a higher workload.
The Covid-19 items can be found in the **Supplementary Material**.
The survey also included the Subjective Wellbeing Index of the World Health Organization [@Braehler2007], which we will not analyze.
Due to a technical error during survey setup, the coping style data of the Erfurter Belastungsinventar [@BoehmKasper2001] cannot be used, so we cannot replicate the mediation of NFC and burnout by active and passive coping.

@@

### *Structural equation model*
Items were reverse coded according to the scale manuals.
The latent factor NFC was computed by subjecting the NCS items to a parcelling procedure following Grass et al. [-@Grass2019], a method that is used in SEM when only relations between but not within constructs are of interest.
Principal component analysis was used to determine the factor loadings of each NCS item onto the first component.
Then, the items were randomly divided into four parcels and the average item loading per parcel was computed.
This was repeated 10,000 times to find the parcelling choice with the smallest difference in average item loadings between parcels.
The latent factor MBI was computed using the three subscales as indicators.
For the demand-resource-ratios, we used three items from the work satisfaction scale each.
The latent factor DTH was indicated by items 4, 8, and 9, DTL by the recoded items 12, 26, and 27, and DRF by items 17, 22, and 24.

@@

  mbi[,keylist$mbi_rpe] <- 7 - mbi[,keylist$mbi_rpe]  # Recode from 1-6 to 6-1
  scs[,keylist$scs] <- 6 - scs[,keylist$scs]          # Recode from 1-5 to 5-1
  scs <- scs - 3                                      # Recode all from 1-5 to -2-+2
  ncs[,keylist$ncs] <- 8 - ncs[,keylist$ncs]          # Recode from 1-7 to 7-1
  ncs <- ncs - 4                                      # Recode all from 1-7 to -3-+3
  ws[,keylist$ws] <- 6 - ws[,keylist$ws]              # Recode from 1-5 to 5-1
  ws <- ws - 3                                        # Recode all from 1-5 to -2-+2
  covb[,c(2,3,4,9)] <- 4 - covb[,c(2,3,4,9)]          # Recode from 1-3 to 3-1
  covb[,8] <- 3 - covb[,8]                            # Recode from 1-2 to 2-1
  # The following recoding is opposite to what is described in the methods section of the paper, which
  # is due to the fact that the questionnaire is originally coded as 1 (false) to 5 (true), but it was
  # coded as 1 (true) to 5 (false) in the SoSciSurvey of the present study.
  dth <- 6 - dth                                      # Recode all from 1-5 to 5-1
  dth <- dth - 3                                      # Recode all from 1-5 to -2-+2
  dtl <- dtl - 3                                      # Recode all from 1-5 to -2-+2
  drf <- 6 - drf                                      # Recode all from 1-5 to 5-1
  drf <- drf -3                                       # Recode all from 1-5 to -2-+2

@@

  # Remove participant 161 in a second version of the data frame (for the supplementary material analysis)
  score_data_no_outlier <- score_data[score_data$mbi < 100, ]

@@

  # structural model
    DTH ~ a1 * NFC
    DTL ~ a2 * NFC
    DRF ~ a3 * NFC
    RPE ~ c * NFC + b1 * DTH + b2 * DTL + b3 * DRF
